Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-02-02 paper.tex
Added figures dir

People us the internet to communicate and share a variety of content. Some entities choose to censor internet connections. These entities may range from individual network administrators to a full nation-state. In this paper, we explore the background and current state of censorship circumvention, and then design and build a system which tackles several of the limitations present in state of the art systems. [LATER: Add xrefs to sections]

We begin by exploring what we mean by censorship circumvention and establishing baseline terminology for this subdiscipline. We then explore the present theory behind approaches to censorship circumvention. We address the ethics of censorship circumvention as a field, and how the field originated and how that affects the current state of the field.

@@

>>>>

People us the internet to communicate and share a variety of content. Some entities choose to censor internet connections. These entities may range from individual network administrators to a full nation-state. In this paper, we explore the state of censorship, existing circumvention sytems, and we design and build a system which tackles several of the limitations present in state of the art systems. [LATER: Add xrefs to sections]

We begin by exploring what we mean by censorship circumvention and establishing baseline terminology for this discipline. We then explore the present theory behind approaches to censorship circumvention. We address the ethics of censorship circumvention as a field, and how the field originated and how that affects the current state of the field.

@@

The term censorship has taken on a life of it's own in the modern social and political context. We are \emph{not} exploring the general connotation of censorship, rather, we are exploring a specific type of censorship that existing in a networking (particularly internetworking) context.
